Computer Science House Constitution

### 2014-03-06 articles.tex
fixed references, added makefile

% This package is useful for debugging label problems 
% Comment out in final revision
%\usepackage{showkeys}

@@

	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting. A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official. All winners are notified and asked to accept or decline their election. Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting. The member(s) initiating the petition present their case to the Executive Board. The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment. If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed. This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office. Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from oce. If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position. A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
\end{enumerate}

@@

>>>>

% This package is useful for debugging label problems 
% Comment out in final revision
\usepackage{showkeys}

@@

	\item The winners are determined by a simple majority vote of the ballots cast as defined in \ref{Simple Majority}, Voting. A quorum of fifty-percent of the number of all members eligible to vote is required for the elections to be official. All winners are notified of their election, and they immediately assume the office for the term of the election. Any office whose winner declines the election, or whose winner was a write-in candidate who does not fulfill the requirements of the elected office, shall remain vacant and a new election process shall begin for that office.

@@

\asection{Impeachment}
\begin{enumerate}
	\item Impeachment of any Executive Board Member may be initiated by petition, in writing, consisting of a minimum number of signatures of current House members equaling or exceeding one-third the Number of Possible Votes as defined in \ref{Total Number of Possible Votes}.
	\item The impeachment petition is then presented at an Executive Board Meeting. The member(s) initiating the petition present their case to the Executive Board. The Executive Board then questions the accused member of the allegations.
	\item The Executive Board votes on the impeachment petition, with all voting members present except the accused member who must be absent and whose vote counts as an abstention, to determine if the allegations stated in the petition are legitimate grounds for impeachment. If the majority of Executive Board votes are negative, the petition and impeachment proceedings are dismissed. This vote may be overridden by an impeachment petition consisting of the grounds for impeachment and a minimum of number of signatures of current House members equaling or exceeding two-thirds the number of all House members currently eligible to vote.
	\item If the majority of the Executive Board votes are positive, or the negative vote was overridden, the petition is presented at the following House Meeting and the accused and accuser(s) again present their cases.
	\item Ballots will then be distributed and a secret ballot House vote shall be held for a minimum of a forty-eight hour period to determine whether or not the member should be removed from office. Votes shall be collected and counted as described in \ref{Balloted Vote}.
	\item A quorum of two-thirds of the Number of Possible Votes is necessary for the vote to be official. A vote equaling or exceeding two-thirds the number of all ballots cast is necessary for the accused officer to be removed from office. If a quorum cannot be reached after two attempts, or the percentage of affirmative votes does not equal or exceed the minimum, impeachment proceedings are dismissed.
	\item If the percentage of affirmative votes equals or exceeds the minimum the impeached officer is relinquished of their position and any benefits thereof and this position is treated like any other vacated position. A new selection and interim duty fulfillment procedure is followed similar to that of a resignation; see \ref{Resignations}.
\end{enumerate}

@@

Decisions made by the Executive Board may be appealed and overturned. To initiate an appeal, a Petition of Appeal must be presented to the Chairman affixed with signatures either one third of Active Members or three voting members of the Executive Board. After the petition is presented, the decision is overturned and will be reevaluated by the Executive Board at the upcoming Executive Board meeting.
